---
title: "Analysis of Eyewitness ranking data: Experiment 2"
author: "Kym McCormick"
date: "15 May 2019"
output:
  pdf_document: default
  word_document: default
  html_notebook: default
---
```{r setup, include=FALSE, results='hide'}

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "C:/GitHub projects/PhD-Thesis/c2 test")


library("psych")
library("tidyverse")
library("MPTinR")
library("readr")
library("knitr")

getwd()

#data <- read.csv("C:/Users/User/Downloads/results_20170720 (1).csv")

data_e2 <- read.csv(file = "experiment_2_Raw.csv")
data_e2$date <- as.Date(data_e2$date)

## Select variables ----
din_e2 <- data_e2 %>%
  select(uid,
         condition, 
         Rank_T1_selectionOrder,
         Test_T1_suspectIdentified,
         demographics_age, 
         demographics_gender, 
         demographics_country,
         date)%>%
  
## Select data from USA only ----  
  filter(demographics_country == "USA", Rank_T1_selectionOrder != "") %>%

## separate the condition variable into separate columns ---
  separate(condition,c("memory","expectation", "target")) %>%
  filter(target == "P")%>%
  
## separate the ranking variable into separate columns ---
  separate(Rank_T1_selectionOrder,c("Rank_1","Rank_2","Rank_3","Rank_4","Rank_5","Rank_6", "Rank_7", "Rank_8"))%>%

drop_na() %>%

## Create columns recording accuracy for each rank
  mutate(R1_Corr = if_else(Rank_1 == "F68", 1,0),
         R2_Corr = if_else(Rank_2 == "F68", 1,0),
         R3_Corr = if_else(Rank_3 == "F68", 1,0),
         R4_Corr = if_else(Rank_4 == "F68", 1,0),
         R5_Corr = if_else(Rank_5 == "F68", 1,0),
         R6_Corr = if_else(Rank_6 == "F68", 1,0),
         R7_Corr = if_else(Rank_7 == "F68", 1,0),
         R8_Corr = if_else(Rank_8 == "F68", 1,0)
         )%>%
  rename(Choice = Test_T1_suspectIdentified)
  
##Create a column of counts
din_e2$n <- if_else(!is.na(din_e2$demographics_country) == "USA", 1,0) 
  
## Convert date to correct format
din_e2$date <- as.Date(din_e2$date, "%Y-%m-%d")

## Convert memory condition to the correct level 
din_e2$memory <- ifelse(din_e2$date == "2019-08-07", "VW", din_e2$memory)

din_e2 <- din_e2 %>% select(-date)
  
```

##Demographics                       
```{r demographics, echo=FALSE}

age <- describe(din_e2$demographics_age)
kable(age)

gender <- din_e2 %>% 
  select(demographics_gender) %>% 
  map(~prop.table(table(.)))

kable(gender)


```

##Counts of correct identifications within each rank position
###Across different levels of memory
```{r, ranking counts by memory, echo=FALSE}
## Create a vector of rank counts ---
Rank_memory <- din_e2 %>% 
  
## Only include target present lineup data ---  
  filter(target == "P") %>%
  
## Separate into levels of memory strength (High and Low) ---  
  group_by(memory)%>%
  
## Sum the correct selection of the target across each rank postion ---  
  summarise(r1 = sum(R1_Corr),
            r2 = sum(R2_Corr),
            r3 = sum(R3_Corr),
            r4 = sum(R4_Corr),
            r5 = sum(R5_Corr),
            r6 = sum(R6_Corr),
            r7 = sum(R7_Corr),
            r8 = sum(R8_Corr)
            ) 

```

###Total counts
```{r, ranking counts total, echo=FALSE}
## Create a vector of overall rank counts ---
Rank_collapsed <- din_e2 %>% 
  
  # Only include target present lineup data ---  
  filter(target == "P") %>%
  
  # Sum the correct selection of the target across each rank postion ---  
  summarise(r1 = sum(R1_Corr),
            r2 = sum(R2_Corr),
            r3 = sum(R3_Corr),
            r4 = sum(R4_Corr),
            r5 = sum(R5_Corr),
            r6 = sum(R6_Corr),
            r7 = sum(R7_Corr),
            r8 = sum(R8_Corr)
            )
## Add new 'Total' level for memory 
Rank_collapsed$memory <- "Total"

## Bind together
Rank <- rbind(Rank_memory,Rank_collapsed)
kable(Rank)

## Return as a structured vector for use in the stat test and fitting function 
Rank_dvector <- Rank %>%
  ungroup() %>%
  select(-memory) %>%
  as.matrix() %>% 
  as.vector %>%
  structure(.Dim= c(4L,8L))

```



##Proportional correct 
```{r, proportional correct, echo=FALSE}
Rank_prop <- din_e2  %>%
  filter(target == "P")%>%
  group_by(memory) %>%
  summarise(Rank_1 = sum(R1_Corr)/sum(n),
            Rank_2 = sum(R2_Corr)/sum(n),
            Rank_3 = sum(R3_Corr)/sum(n),
            Rank_4 = sum(R4_Corr)/sum(n),
            Rank_5 = sum(R5_Corr)/sum(n),
            Rank_6 = sum(R6_Corr)/sum(n),
            Rank_7 = sum(R7_Corr)/sum(n),
            Rank_8 = sum(R8_Corr)/sum(n),
            n = n()
            )%>%
  ungroup()%>%
  select(-n)
```

##Conditional rank probabilities
```{r, conditional rank probabilities, echo=FALSE}
## Create a vector of conditional rank probabilities ---
Cond_Cum_R <- din_e2 %>% 
  
## Only include target present lineup data ---  
  filter(target == "P") %>%
  
## Separate into levels of memory strength (High and Low) ---  
  group_by(memory)%>%
## Sum the correct selection of the target across each rank postion ---  
  summarise(r1 = sum(R1_Corr),
            r2 = sum(R2_Corr),
            r3 = sum(R3_Corr),
            r4 = sum(R4_Corr),
            r5 = sum(R5_Corr),
            r6 = sum(R6_Corr),
            r7 = sum(R7_Corr),
            r8 = sum(R8_Corr),
            n = r1+r2+r3+r4+r5+r6+r7+r8
            ) %>% 

## Calcluate conditional rank probabilities ---
  mutate(c1 = r1/n,
         c2 = r2/(n-r1),
         c3 = r3/(n-r1-r2),
         c4 = r4/(n-r1-r2-r3),
         c5 = r5/(n-r1-r2-r3-r4),
         c6 = r6/(n-r1-r2-r3-r4-r5),
         c7 = r7/(n-r1-r2-r3-r4-r5-r6),
         c8 = r8/(r8)
         ) %>%
  select(-r1,-r2,-r3,-r4,-r5,-r6,-r7,-r8,-n)
kable(Cond_Cum_R)

## Create a structured vector
Cond_Cum_RV <- Cond_Cum_R %>%
  ungroup()%>%
  select(-memory) %>%
  as.matrix() %>%
  as.vector() %>%
  structure(.Dim = c(3L,8L))

## Transform into dataframe for ggplot2
Strong <- as.data.frame(t(Cond_Cum_R[1,2:9]))
Strong$Rank <- c(1:8)
Strong$Memory <- c(rep("Strong",2))

Weak <- as.data.frame(t(Cond_Cum_R[3,2:9]))
Weak$Rank <- c(1:8)
Weak$Memory <- c(rep("Weak",2))

VeryWeak <- as.data.frame(t(Cond_Cum_R[2,2:9]))
VeryWeak$Rank <- c(1:8)
VeryWeak$Memory <- c(rep("VeryWeak",2))

ci <- rbind(Strong,Weak,VeryWeak)

ci <- ci %>%
  rename(ci = V1)
```

```{r, cumulative accuracy s-w, echo=FALSE}
ciSVW <- ci %>%
  filter(Memory != "VeryWeak")

ciPlot1 <- ggplot(ciSVW,aes(x = Rank, y = ci))+
  geom_line(aes(linetype = Memory)) +
   geom_point(aes(shape = Memory), size = 3) +
  scale_shape_manual(values = c(16, 1)) +
  theme_classic()+
  theme(legend.position="bottom")+
  scale_x_continuous(breaks = scales::pretty_breaks(n = 8)) + 
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))
```
```{r, cumulative accuracy s-vw, echo=FALSE}
ciSW <- ci %>%
  filter(Memory != "Weak")

ciPlot2 <- ggplot(ciSW,aes(x = Rank, y = ci))+
  geom_line(aes(linetype = Memory)) +
   geom_point(aes(shape = Memory), size = 3) +
  scale_shape_manual(values = c(16, 1)) +
  theme_classic() +
  theme(legend.position="bottom") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 6)) + 
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))
```

```{r, cumulative accuracy s-w and s-vw, echo=FALSE}
ciWVW <- ci %>%
  filter(Memory != "Strong")
ciS <- ci %>%
  filter(Memory == "Strong")%>%
  rename(Strong = Memory)

labels <- c(VeryWeak = "Degraded encoding", Weak = "Interference")

ciPlot_e2 <- ggplot(ciWVW,aes(x = Rank, y = ci))+
  geom_line(linetype = 2) +
  geom_point(shape = 1, size = 3) +
  geom_line(data = ciS, linetype = 1)+
  geom_point(data = ciS, shape = 16, size = 3)+
  ylab("Conditional Accuracy")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.title.y = element_text(size=12),
        axis.title.x = element_text(size=12),
        strip.text.x = element_text(size=12),
        strip.background = element_rect(colour="black", fill=("0"))
        ) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 6)) + 
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
  facet_grid(.~Memory, labeller=labeller(Memory = labels))+ 
  theme(aspect.ratio = 1)




ciPlot_e2

```



##Cumulative accuracy memory-choice interaction

```{r, cumulative accuracy memory-choice interaction, echo=FALSE}
##Setting up ranking to look at between choosers and non-choosers
Choosing <- din_e2 %>%
  select(memory, expectation, target, R1_Corr, R2_Corr, R3_Corr, R4_Corr, R5_Corr, R6_Corr, R7_Corr, R8_Corr, Choice)%>%
  mutate(choose = if_else(Choice != "Silhouette", 1, 0))
  
## Create a vector of conditional rank probabilities ---
Choosing <- Choosing %>% 
  
## Only include target present lineup data ---  
  filter(target == "P") %>%
  
## Separate into levels of memory strength (High and Low) ---  
  group_by(choose, memory)%>%
## Sum the correct selection of the target across each rank postion ---  
  summarise(r1 = sum(R1_Corr),
            r2 = sum(R2_Corr),
            r3 = sum(R3_Corr),
            r4 = sum(R4_Corr),
            r5 = sum(R5_Corr),
            r6 = sum(R6_Corr),
            r7 = sum(R7_Corr),
            r8 = sum(R8_Corr),
            n = r1+r2+r3+r4+r5+r6+r7+r8
            ) %>% 
## Calcluate conditional rank probabilities ---
  mutate(c1 = r1/n,
         c2 = r2/(n-r1),
         c3 = r3/(n-r1-r2),
         c4 = r4/(n-r1-r2-r3),
         c5 = r5/(n-r1-r2-r3-r4),
         c6 = r6/(n-r1-r2-r3-r4-r5),
         c7 = r7/(n-r1-r2-r3-r4-r5-r6),
         c8 = r8/(r8)
         ) 

## Create a dataframe from above for use in ggplot
StrongChoose <- as.data.frame(t(Choosing[4,12:19]))
StrongChoose$Rank <- c(1:8)
StrongChoose$Memory <- c(rep("Strong",2))
StrongChoose$Choose <- c(rep("Identify",2))

StrongNoChoose <- as.data.frame(t(Choosing[1,12:19]))
StrongNoChoose$Rank <- c(1:8)
StrongNoChoose$Memory <- c(rep("Strong",2))
StrongNoChoose$Choose <- c(rep("Reject",2))

WeakChoose <- as.data.frame(t(Choosing[6,12:19]))
WeakChoose$Rank <- c(1:8)
WeakChoose$Memory <- c(rep("Weak",2))
WeakChoose$Choose <- c(rep("Identify",2))

WeakNoChoose <- as.data.frame(t(Choosing[3,12:19]))
WeakNoChoose$Rank <- c(1:8)
WeakNoChoose$Memory <- c(rep("Weak",2))
WeakNoChoose$Choose <- c(rep("Reject",2))

VeryWeakChoose <- as.data.frame(t(Choosing[4,12:19]))
VeryWeakChoose$Rank <- c(1:8)
VeryWeakChoose$Memory <- c(rep("Very Weak",2))
VeryWeakChoose$Choose <- c(rep("Identify",2))

VeryWeakNoChoose <- as.data.frame(t(Choosing[2,12:19]))
VeryWeakNoChoose$Rank <- c(1:8)
VeryWeakNoChoose$Memory <- c(rep("Very Weak",2))
VeryWeakNoChoose$Choose <- c(rep("Reject",2))

ciChoose <- rbind(StrongChoose,StrongNoChoose,WeakChoose,WeakNoChoose,VeryWeakChoose,VeryWeakNoChoose)

ciChoose <- ciChoose %>%
  rename(ci = V1)

## Create a structured vector
Choosing <- Choosing %>%
  ungroup()%>%
  select(-choose,-memory,-n) %>%
  as.matrix() %>%
  as.vector() %>%
  structure(.Dim = c(6L,16L))

Choosing <- Choosing[,9:16]


```
###Plot by choosers and memory
```{r, echo=FALSE}
labels <- c(Strong = "Normal","Very Weak" = "Degraded encoding", Weak = "Interference")

ciChoosePlot_e2 <- ggplot(ciChoose,aes(x = Rank, y = ci))+
  geom_line(data = ciS, linetype = 1, color = "light grey")+
  geom_point(data = ciS, shape = 16, size = 3, color = "light grey")+
  geom_line(linetype = 1) +
  geom_point(shape = 16, size = 3) +
  ylab("Conditional Accuracy")+
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.title.y = element_text(size=12),
        axis.title.x = element_text(size=12),
        strip.text = element_text(size=12),
        strip.background = element_rect(colour="black", fill=("0"))
        ) +

  scale_x_continuous(breaks = scales::pretty_breaks(n = 6)) + 
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
  facet_grid(Choose~Memory, labeller=labeller(Memory = labels)) + 
  theme(aspect.ratio = 1)

ciChoosePlot_e2



```



#Estimation of UV-SDT parameters

Model
```{r, Model}

expSDTrank <- function(Q, param.names, n.params, tmp.env){
  n <- 8
  e <- vector("numeric", n)
  mu <- Q[1]
 # ss <- Q[2]
  G <- function(x,i) {
    (pnorm(x)^(n-i))*dnorm(x, mean = mu, sd = 1)*(1-pnorm(x))^(i-1)*choose(n-1, i-1)
    }
    
  for (ii in 1:n) {
    e[ii] <- integrate(G,-Inf,Inf,i = ii, rel.tol = .Machine$double.eps^0.5)$value
    }
  return(e)
}
```

Fitting function
```{r, Fitting function}

SDTrank <- function(Q, data, param.names, n.params, tmp.env, lower.bound, upper.bound){
  e <- expSDTrank(Q, param.names, n.params, tmp.env)
  LL <- -sum(data[data!=0]*log(e[data!=0]))
  return(LL)
  }
```
###Results
Strong memory
```{r, echo=FALSE}
Rank_strong <- fit.mptinr(
  data = Cond_Cum_RV[1,], 
  objective = SDTrank, 
  param.names = c("mu"), 
  categories.per.type = 8, 
  prediction = expSDTrank, 
  lower.bound = c(0), 
  upper.bound = Inf,
  starting.values = c(1)
)

rank.strong.para <- Rank_strong$parameters%>%
  select(estimates)
```

Weak memory
```{r, echo=FALSE}
Rank_weak <- fit.mptinr(
  data = Cond_Cum_RV[3,], 
  objective = SDTrank, 
  param.names = c("mu", "sigma"), 
  categories.per.type = 8, 
  prediction = expSDTrank, 
  lower.bound = c(0,0.1), 
  upper.bound = Inf,
  starting.values = c(1,1)
)

rank.weak.para <- Rank_weak$parameters%>%
  select(estimates)
```
Very Weak memory
```{r, echo=FALSE}
Rank_Very_weak <- fit.mptinr(
  data = Cond_Cum_RV[2,], 
  objective = SDTrank, 
  param.names = c("mu", "sigma"), 
  categories.per.type = 8, 
  prediction = expSDTrank, 
  lower.bound = c(0,0.1), 
  upper.bound = Inf,
  starting.values = c(1,1)
)

rank.very.weak.para <- Rank_Very_weak$parameters
%>%   select(estimates)

rank.very.weak.para
```

Combined
```{r, echo=FALSE}
Rank_comb <- fit.mptinr(
  data = Rank_dvector[3,], 
  objective = SDTrank, 
  param.names = c("mu", "sigma"), 
  categories.per.type = 8, 
  prediction = expSDTrank, 
  lower.bound = c(0,0.1), 
  upper.bound = Inf,
  starting.values = c(1,1)
)

rank.comb.para <- Rank_comb$parameters%>%
  select(estimates)

```
```{r, echo=FALSE}
rank.para <- cbind(rank.weak.para,rank.comb.para,rank.strong.para)
colnames(rank.para) <- c("weak", "combined", "strong")
```

```{r, echo=FALSE}
svg("C:/GitHub projects/PhD-Thesis/c2 test/Output/ciPlot_e2.svg")
print(ciPlot_e2) 
svg("C:/GitHub projects/PhD-Thesis/c2 test/Output/ciChoosePlot_e2.svg")
print(ciChoosePlot_e2)       # Plot 1 --> in the first page of PDF
dev.off() 
 
```


