---
title: "Untitled"
author: "Kym McCormick"
date: "28/10/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(ggplot2)
x <- vector()
```

# Ranking Probabilities

For an $n$-item lineup consisting of one target and $n-1$ foils, let $t$ be the probability that the eyewitness will detect the target (as the target) and let $f$ be the probability that they will detect a foil (as a foil). Let $[n]=\{1,\ldots,n\}$.

Suppose for a given eyewitness that $k \in [n-1]$ foils are not detected. We assume that the target is never detected as a foil. Then the \textit{effective lineup size} is $x=k+1$. Let $s(x)$ be the probability that the effective lineup size is $x$. Then

$$s(x) = \binom{n-1}{x-1}(1-f)^{x-1}f^{n-x}.$$

## Rank probability

Suppose that the target is not detected as a target and the  effective lineup size is $x$ items. Then the target has an equal probability of being assigned a rank from 1 to $x$. Let $p(r)$ be the probability that the target is assigned rank $r \in [n]$, given it is not detected. Then 

\begin {equation} \label {eq:eq1}
p(r)=\sum^{n}_{x=r}\frac{s(x)}{x}.
\end {equation}

The function $p(r)$:
```{r}
b <- function(r, n, f){
  for (i in r:n)
    x[i] <- choose(n-1, i-1)*(1-f)^(i-1)*f^(n-i)/i
  return(sum(x, na.rm = TRUE))
}

p <- function(n, f){
  for (i in 1:n)
    x[i] <- b(i, n, f)
  return(x)
}

```



We assume that if the target is detected it is assigned rank 1. Let $q(r)$ be the probability that a target is assigned rank $r \in [n]$. Then

\begin {equation}\label {eq:eq2}
q(r):\left\{
   \begin {aligned}
   t+(1-t)p(r)&,\; r=1  \\
   (1-t)p(r)&, \; r>1\\
   \end {aligned}
   \right.
\end {equation}



# Conditional Ranking Probabilities

Let $Q(r)$ be the cumulative sum,
\begin {equation} \label {eq:eq3}
Q(r) = \sum^{r}_{i=1}q(i).
\end {equation}

Let $c(r)$ be the conditional probability that the target is assigned rank $r$ given that it has not been assigned any rank less than $r$. Then

\begin {equation}\label {eq:eq4}
c(r):\left\{
   \begin {aligned}
   q(r)&,\; r=1  \\
   \frac{q(r)}{(1-Q(r-1))}&, \; r>1\\
   \end {aligned}
   \right.
\end {equation}

# Theorem

We want to show that $c(2)<c(3)$. Suppose $c(2)<c(3)$. I thought I would try a brute force approach (although unsuccessfully). From Equations \eqref{eq:eq3} and \eqref{eq:eq4},
$$\frac{q(2)}{1-q(1)}<\frac{q(3)}{1-q(1)-q(2)}$$
\noindent From Equation \eqref{eq:eq4},
$$\frac{(1-t)p(2)}{1-t-(1-t)p(1)}<\frac{(1-t)q(3)}{1-t-(1-t)p(1)-(1-t)p(2)}$$
\noindent For $t<1$,
$$\frac{p(2)}{1-p(1)}<\frac{p(3)}{1-p(1)-p(2)}$$

If the theorem is true, then $c(2)/c(3)$ is $<1$ for all values of $n$ and $f$.

## Demonstration of theorem

The function $c(2)/c(3)$:
```{r}
c2c3ratio <- function(n, f){
  x <- p(n,f)
  x[n+1] <- (x[2]/(1-x[1]))/(x[3]/(1-x[1]-x[2]))
  return(x[n+1])
}
# Create a vector of values of f
s <- seq(0,.99999, by=.001) 

# The function calculating c(2)/c(3) for each value in vector s
Ratio <- function(n){
  for (i in 1:length(s)) 
    x[i] <- c2c3ratio(n,s[i])
  return(x)
}


```


Draw the function $c(2)/c(3)$ for $n \in \{4,5,6,7,8,10,20,50,100,250\}$:







```{r}
n4 <- Ratio(4)
n5 <- Ratio(5)
n6 <- Ratio(6)
n7 <- Ratio(7)
n8 <- Ratio(8)
n10 <- Ratio(10)
n20 <- Ratio(20)
n50 <- Ratio(50)
n100 <- Ratio(100)
n250 <- Ratio(250)
n4 <- as.data.frame(cbind(n4,s))
n5 <- as.data.frame(cbind(n5,s))
n6 <- as.data.frame(cbind(n6,s))
n7 <- as.data.frame(cbind(n7,s))
n8 <- as.data.frame(cbind(n8,s))
n10 <- as.data.frame(cbind(n10,s))
n20 <- as.data.frame(cbind(n20,s))
n50 <- as.data.frame(cbind(n50,s))
n100 <- as.data.frame(cbind(n100,s))
n250 <- as.data.frame(cbind(n250,s))

ggplot()+
  geom_line(data = n4, aes(y=n4, x=s))+
  geom_line(data = n5, aes(y=n5, x=s))+
  geom_line(data = n6, aes(y=n6, x=s))+
  geom_line(data = n7, aes(y=n7, x=s))+
  geom_line(data = n8, aes(y=n8, x=s))+
  geom_line(data = n10, aes(y=n10, x=s))+
  geom_line(data = n20, aes(y=n20, x=s))+
  geom_line(data = n50, aes(y=n50, x=s))+
  geom_line(data = n100, aes(y=n100, x=s))+
  geom_line(data = n250, aes(y=n250, x=s))+
  labs(subtitle="Ratio of conditional second to conditional third choices for all values of f",        x="f",        y="Ratio"       ) +
  theme_bw()



```

