---
title: "Wells' partial memory model"
author: "Kym McCormick and John Dunn"
date: "28/10/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(ggplot2)
x <- vector()
```

# Ranking Probabilities: Wells partial memory model

For an $n$-item lineup consisting of one target and $n-1$ foils, let $t$ be the probability that the eyewitness will detect the target (as the target) and let $f$ be the probability that they will detect a foil (as a foil). Let $[n]=\{1,\ldots,n\}$.

Suppose for a given eyewitness that $k \in [n-1]$ foils are not detected. We assume that the target is never detected as a foil. Then the \textit{effective lineup size} is $x=k+1$. Let $s(x)$ be the probability that the effective lineup size is $x$. Then

$$s(x) = \binom{n-1}{x-1}(1-f)^{x-1}f^{n-x}.$$



Suppose that the target is not detected as a target and the  effective lineup size is $x$ items. Then the target has an equal probability of being assigned a rank from 1 to $x$. Let $p(r)$ be the probability that the target is assigned rank $r \in [n]$, given it is not detected. Then 

\begin {equation} \label {eq:eq1}
p(r)=\sum^{n}_{x=r}\frac{s(x)}{x}.
\end {equation}

The function $p(r)$:
```{r}
b <- function(r, n, f){
  for (i in r:n)
    x[i] <- choose(n-1, i-1)*(1-f)^(i-1)*f^(n-i)/i
  return(sum(x, na.rm = TRUE))
}

p <- function(n, f){
  for (i in 1:n)
    x[i] <- b(i, n, f)
  return(x)
}

```



We assume that if the target is detected it is assigned rank 1. Let $q(r)$ be the probability that a target is assigned rank $r \in [n]$. Then

\begin {equation}\label {eq:eq2}
q(r):\left\{
   \begin {aligned}
   t+(1-t)p(r)&,\; r=1  \\
   (1-t)p(r)&, \; r>1\\
   \end {aligned}
   \right.
\end {equation}



# Conditional Ranking Probabilities

Let $Q(r)$ be the cumulative sum,
\begin {equation} \label {eq:eq3}
Q(r) = \sum^{r}_{i=1}q(i).
\end {equation}

Let $c(r)$ be the conditional probability that the target is assigned rank $r$ given that it has not been assigned any rank less than $r$. Then

\begin {equation}\label {eq:eq4}
c(r):\left\{
   \begin {aligned}
   q(r)&,\; r=1  \\
   \frac{q(r)}{(1-Q(r-1))}&, \; r>1\\
   \end {aligned}
   \right.
\end {equation}

# Theorem

We want to show that $c(2)<c(3)$. Suppose $c(2)<c(3)$. I thought I would try a brute force approach (although unsuccessfully). From Equations \eqref{eq:eq3} and \eqref{eq:eq4},
$$\frac{q(2)}{1-q(1)}<\frac{q(3)}{1-q(1)-q(2)}$$
\noindent From Equation \eqref{eq:eq4},
$$\frac{(1-t)p(2)}{1-t-(1-t)p(1)}<\frac{(1-t)q(3)}{1-t-(1-t)p(1)-(1-t)p(2)}$$
\noindent For $t<1$,
$$\frac{p(2)}{1-p(1)}<\frac{p(3)}{1-p(1)-p(2)}$$

If the theorem is true, then $c(2)/c(3)$ is $<1$ for all values of $n$ and $f$.

## Demonstration of theorem

The function $c(2)/c(3)$:
```{r}

c2c3ratio <- function(n, f){
  x <- p(n,f)
  x[n+1] <- (x[2]/(1-x[1]))/(x[3]/(1-x[1]-x[2]))
  return(x[n+1])
}

```

# Ranking probability: Thurstone's rank orker model


```{r}
expSDTrank <- function(Q,n){
  e <- vector("numeric", n)
  mu <- Q[1]
 # ss <- Q[2]
  G <- function(x,i) {
    (pnorm(x)^(n-i))*dnorm(x, mean = mu, sd = 1)*(1-pnorm(x))^(i-1)*choose(n-1, i-1)
    }
    
  for (ii in 1:n) {
    e[ii] <- integrate(G,-Inf,Inf,i = ii, rel.tol = .Machine$double.eps^0.5)$value
    }
  return(e)
}

SDTc2c3ratio <- function(Q,n){
  x <- expSDTrank(Q,n)
  x[n+1] <- (x[2]/(1-x[1]))/(x[3]/(1-x[1]-x[2]))
  return(x[n+1])
}


SDTc2c3ratio(.5 ,8)
```

Draw the function $c(2)/c(3)$ for $n=8$:

```{r}
#Set the value of n
n <- 8
Q <- 1
# Create a vector of values of f and d'
s <- seq(0,.99999, by=.001) 
dprime <- seq(0,4, by=.01)

# The function calculating c(2)/c(3) for each value in vector s
RatioWPM <- function(n){
  for (i in 1:length(s)) 
    x[i] <- c2c3ratio(n,s[i])
  return(x)
}

# The function calculating c(2)/c(3) for each value in vector dprime
RatioSDT <- function(n){
  for (i in 1:length(dprime)) 
    x[i] <- SDTc2c3ratio(dprime[i],n)
  return(x)
}

# Create a vector of c(2)/c(3) ratios for all values of f where n = n
WPM <- RatioWPM(n)
WPM <- as.data.frame(WPM)
WPM$f <- s

# Create a vector of c(2)/c(3) ratios for all values of f where n = n
SDT <- RatioSDT(n)
SDT <- as.data.frame(SDT)
SDT$"d'" <- dprime

# Draw the function for n = n
plot = ggplot() + 
  geom_line(data=WPM, aes(x=s,y=WPM))+
  #geom_line(data=SDT,aes(x=dprime,y=SDT))+
  labs(subtitle="Ratio of conditional second to conditional third choices for all values of f", 
       x="f", 
       y="Ratio"
       ) +
  theme_bw()
plot
```


Determine the minimum value of $c(2)/c(3)$ and identify the value of $f$ where this occurs:

```{r}
optimise(f=c2c3ratio, c(0,1), maximum = FALSE, n=n)
#optimise(SDTc2c3ratio, c(0,4), maximum = TRUE, n=n)
```

```{r}
h <- 10000
foil <- runif(h)
k <- floor(runif(h, min = 3, max = 11))
t <- runif(h)
MC <- vector()

 for (i in 1:length(k)) {
    MC[i] <- c2c3ratio(k[i],foil[i])
}

MC <- as.data.frame(MC)
MC$n <- k
MC$f <- foil

ggplot(MC,aes(x=f, y=MC))+
  geom_point()+
  theme_bw()
```

