---
title: "SDT c2/c3 ratio"
author: "Kym McCormick"
date: "30/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r cars}
```{r}
expSDTrank <- function(Q,n){
  e <- vector("numeric", n)
  mu <- Q[1]
 # ss <- Q[2]
  G <- function(x,i) {
    (pnorm(x)^(n-i))*dnorm(x, mean = mu, sd = 1)*(1-pnorm(x))^(i-1)*choose(n-1, i-1)
    }
    
  for (ii in 1:n) {
    e[ii] <- integrate(G,-Inf,Inf,i = ii, rel.tol = .Machine$double.eps^0.5)$value
    }
  return(e)
}

SDTc2c3ratio <- function(Q,n){
  x <- expSDTrank(Q,n)
  x[n+1] <- (x[2]/(1-x[1]))/(x[3]/(1-x[1]-x[2]))
  return(x[n+1])
}


SDTc2c3ratio(.5 ,8)
```



```{r}
#Set the value of n
n <- 8
Q <- 1
# Create a vector of values of f and d'
dprime <- seq(0,4, by=.01)


# The function calculating c(2)/c(3) for each value in vector dprime
RatioSDT <- function(n){
  for (i in 1:length(dprime)) 
    x[i] <- SDTc2c3ratio(dprime[i],n)
  return(x)
}

# Create a vector of c(2)/c(3) ratios for all values of d' where n = n
SDT <- RatioSDT(n)
SDT <- as.data.frame(SDT)
SDT$"d'" <- dprime

# Draw the function for n = n
plot = ggplot() + 
  geom_line(data=SDT,aes(x=dprime,y=SDT))+
  labs(subtitle="Ratio of conditional second to conditional third choices for all values of f", 
       x="f", 
       y="Ratio"
       ) +
  theme_bw()
plot
```

