---
title: "Eyewitness identification data analysis"
author: "Kym McCormick"
date: "15 May 2019"
output:
  word_document: default
  pdf_document: default
  html_notebook: default
---
```{r setup, include=FALSE, results='hide'}

knitr::opts_chunk$set(echo = TRUE)


library("psych", lib.loc="~/R/win-library/3.5")
library("tidyverse", lib.loc="~/R/win-library/3.5")

library("MPTinR", lib.loc="~/R/win-library/3.5")

```

```{r data wrangling}
setwd("C:/Users/mccormick/GitHub/PhD-Thesis")

data <- read.csv("data/Experiment 3/experiment3data.csv")


din <- data %>%
  select(uid,
         condition, 
         Test_T1_suspectIdentified, 
         confidence_rating, 
         demographics_age, 
         demographics_gender, 
         demographics_country)%>%
  filter(demographics_country == "USA", !is.na(confidence_rating)) %>%
  separate(condition,c("memory","expectation","target")) %>%
  mutate(CID = if_else(target == "P" & Test_T1_suspectIdentified == "F68", 1, 0),
         Miss = if_else(target == "P" & Test_T1_suspectIdentified == "Silhouette", 1, 0),
         TPFoilID = if_else(target == "P" & Test_T1_suspectIdentified != "F68" & Test_T1_suspectIdentified != "Silhouette", 1, 0),
         CR = if_else(target == "A" & Test_T1_suspectIdentified == "Silhouette", 1, 0),
         TAFoilID = if_else(target == "A" & Test_T1_suspectIdentified != "Silhouette", 1, 0)
         )


#din = mutate(din, decile = ntile(din$confidence_rating,10))

din
```


```{r}
## There are twice the number of target present lineups than target absent lineups. To rebalance this in a way that preserves the groupings of confidence intervals, I have chosen to double the Target Absent data before grouping into equal sized confidence rating bins

## Separate data into target present and absent dataframes ---
Ratings_Absent <- din %>%
  filter(target == "A")

Ratings_Present <- din %>%
  filter(target == "P")

## Bind back together, doubling up on the target absent group ---
## NOTE THAT DUPLICATES MAY BE REMOVED USING THE UID NUMBERS ---
Ratings <- rbind(Ratings_Absent,Ratings_Absent,Ratings_Present)

## Group chooser confidence into decile confidence rating bins
din_mod_choose <- Ratings %>%
  filter(Test_T1_suspectIdentified != "Silhouette") %>%
  mutate(decile_cr = ntile(confidence_rating,10)
  )

## Group non-chooser confidence into a single zero confidence rating bin
din_mod_nochoose <- Ratings %>%
  filter(Test_T1_suspectIdentified == "Silhouette") %>%
  mutate(decile_cr = 0)
            
## Bind chooser and non-chooser data back together
din_mod <- rbind(din_mod_choose, din_mod_nochoose)
din_mod
```

```{r}
## Check the grouping of the confidence rating deciles to ensure evenness
Rating_prop <- din_mod %>%
  select(decile_cr) %>%
  map(~prop.table(table(.))
            )
Rating_prop

```

##Demographics                         ##
```{r demographics}
#length(unique(din$uid))

describe(din$demographics_age)

demo <- din %>% 
  select(demographics_gender) %>% 
  map(~prop.table(table(.)))

demo
```
##Identification Data

 
Number of Correct and False IDs per confidence decile

```{r}

ID_dat <- din_mod %>% 
  group_by(decile_cr) %>%
  summarise(
    Miss = sum(Miss),
    TPFID = sum(TPFoilID),
    Correct_ID = sum(CID),
    CR = sum(CR),
    TAFID = sum(TAFoilID)*7/8,
    False_ID = sum(TAFoilID)/8,
    n = n()
    )  

ID_dat

```
Vector of Correct ID and False ID counts for each confidence decile. Note that False ID counts are the number of identifications from target absent lineups divided by the number of items within the lineup (n = 8)

```{r}

ID_dvector <- din_mod %>% 
  group_by(decile_cr) %>%
  summarise(
    Miss = sum(Miss)/n(),
    TPFID = sum(TPFoilID)/n(),
    Correct_ID = sum(CID)/n(),
    CR = sum(CR)/n(),
    TAFID = sum(TAFoilID)*7/8/n(),
    False_ID = sum(TAFoilID)/8/n(),
    )  

 # select(-decile,-n,-Miss,-TPFID,-CR,-TAFID) %>% 
 #as.matrix() %>% 
  #t() %>% 
  #as.vector #%>%
  #structure(.Dim= c(10L,6L))

ID_dvector


```
Vector of CIDs and FIDs for each confidence decile. Note that FIDs are calculated using Wixted & Mickes method, as per above.

```{r}
## Creating HIT/FA pairs for ROC
TP <- count(din_mod,target == "P")
TP

HIT_FA_prop <- ID_dat %>%
  filter(decile_cr != 0) %>%
  select(Correct_ID, False_ID) %>%
  transform(Correct_ID = Correct_ID/1270,
            False_ID = False_ID/1377) 

HIT_FA_prop <- HIT_FA_prop[10:1,]

HIT_FA_prop
```
```{r}
ROC <- HIT_FA_prop %>%
  transform(Correct_ID = cumsum(Correct_ID),
            False_ID = cumsum(False_ID)
  )
ROC
  
```

```{r}
HIT <- ROC[1:10,1]
HIT
FA <- ROC[1:10,2]
```


##Estimating UV-SDT model parameters



```{r}
IndObvSDT_eyewit <- function(Q, data, param.names, n.params, tmp.env){

  n <- 8 
  mean <- Q[1]
  sd <- Q[2]
  cr <- c(Q[3:12])  #confidence criterion

  v <- vector()

  for (i in 1:length(cr)) {
    TID <-  integrate(
      f = function(x){
        dnorm(x,mean,sd)*(pnorm(x,0,1)^(n-1))
        },
      lower = cr[i],
      upper = Inf
      )$value
    FID <- (n-1)*(integrate(
      f = function(x) {
        dnorm(x,0,1)*pnorm(x,mean,sd)*(pnorm(x,0,1)^(n-2))
        },
      lower = cr[i],
      upper = Inf
      )$value
    )
    FA <- (1-pnorm(cr[i])^n)/n
    #TD <- 1-(pnorm((mean-cr[i])/sd)*(pnorm(cr[i])^(n-1)))

    I <- c(
      t(
        cbind(
          (1-(FID+TID)),#Miss (TP)
          FID,          #Foil ID (TP)
          TID,          #Target ID
          1-FA,           #Correct Rejection (TA)
          FA*(n-1)/n,     #Foil ID (TA)
          FA              #False ID (TA)
        )
      )
    )

v <- cbind(v,I)


  }

  Outcomes <- c(t(v))
  return(Outcomes)
  

}


IndObvMLE <- function(Q, data, param.names, n.params, tmp.env, lower.bound, upper.bound){

    e <- IndObvSDT_eyewit(Q, param.names, n.params, tmp.env)
    LL <- -sum(data[data!=0]*log(e[data!=0]))

   

    return(LL)

}

```

```{r}

fit_kafc <- fit.mptinr(

    data = ID_cum_vector,

    objective = IndObvMLE,

    param.names = c("mu", "sigma", "cr1", "cr2", "cr3", "cr4", "cr5", "cr6", "cr7", "cr8", "cr9", "cr10"),

    categories.per.type = c(6,6,6,6,6,6,6,6,6,6),

    prediction = IndObvSDT_eyewit,

    lower.bound = c(0,0.1,-Inf,-Inf,-Inf,-Inf,-Inf,-Inf,-Inf,-Inf,-Inf,-Inf),

    upper.bound = Inf,

    n.optim = 5,

    #starting.values = c(1,1,1,1,1,1,1,1,1,1,1,1,1,1),

    show.messages = FALSE

)

 

fit_kafc$goodness.of.fit

fit_kafc$parameters
```


```{r}
UVSDT_eyewit <- function(Q, data, param.names, n.params, tmp.env){

  n <- 8 
  mean <- Q[1]
  sd <- Q[2]
  cr <- c(Q[3:12])  #confidence criterion

  v <- vector()

  for (i in 1:length(cr)) {
    CID <-  integrate(
      f = function(x){
        dnorm(x,mean,sd)*(pnorm(x,0,1)^(n-1))
        },
      lower = cr[i],
      upper = Inf
      )$value
        
    FA <- (1-pnorm(cr[i])^n)/n

    I <- c(
      t(
        cbind( (1-CID), CID, 1-(FA), FA )
      )
    )

v <- cbind(v,I)
#print(v)

  }

  Outcomes <- c(t(v))
  return(Outcomes)
  

}
 

IndObvMLE2 <- function(Q, data, param.names, n.params, tmp.env, lower.bound, upper.bound){

    e <- UVSDT_eyewit(Q, param.names, n.params, tmp.env)
    LL <- -sum(data[data!=0]*log(e[data!=0]))

   

    return(LL)

}
```

```{r}

fit_kafc <- fit.mptinr(

    data = ID_cum_vector2,

    objective = IndObvMLE2,

    param.names = c("mu", "sigma", "cr1", "cr2", "cr3", "cr4", "cr5", "cr6", "cr7", "cr8", "cr9", "cr10"),

    categories.per.type = c(4,4,4,4,4,4,4,4,4,4),

    prediction = UVSDT_eyewit,

    lower.bound = c(0,0.1,-Inf,-Inf,-Inf,-Inf,-Inf,-Inf,-Inf,-Inf,-Inf,-Inf),

    upper.bound = Inf,

    n.optim = 5,

    starting.values = c(0,0,0,0,0,0,0,0,0,0,0,0),

    show.messages = FALSE

)

 

fit_kafc$goodness.of.fit

fit_kafc$parameters
```


```{r}
n <- 8
UVSDT <-"
pnorm((cr1 - mu)/ss)
pnorm((cr1+cr2 - mu)/ss) - pnorm((cr1 - mu)/ss)
pnorm((cr1+cr2+cr3 - mu)/ss) - pnorm((cr1+cr2 - mu)/ss)
pnorm((cr1+cr2+cr3+cr4 - mu)/ss) - pnorm((cr1+cr2+cr3 - mu)/ss)
pnorm((cr1+cr2+cr3+cr4+cr5 - mu)/ss) - pnorm((cr1+cr2+cr3+cr4 - mu)/ss)
pnorm((cr1+cr2+cr3+cr4+cr5+cr6 - mu)/ss) - pnorm((cr1+cr2+cr3+cr4+cr5 - mu)/ss)
pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7 - mu)/ss) - pnorm((cr1+cr2+cr3+cr4+cr5+cr6 - mu)/ss)
pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7+cr8 - mu)/ss) - pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7 - mu)/ss)
pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7+cr8+cr9 - mu)/ss) - pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7+cr8 - mu)/ss)
pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7+cr8+cr9+cr10 - mu)/ss) - pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7+cr8+cr9 - mu)/ss)

1 - pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7+cr8+cr9+cr10 - mu)/ss)

pnorm((cr1))
pnorm((cr1+cr2)) - pnorm((cr1))
pnorm((cr1+cr2+cr3)) - pnorm((cr1+cr2))
pnorm((cr1+cr2+cr3+cr4)) - pnorm((cr1+cr2+cr3))
pnorm((cr1+cr2+cr3+cr4+cr5)) - pnorm((cr1+cr2+cr3+cr4))
pnorm((cr1+cr2+cr3+cr4+cr5+cr6)) - pnorm((cr1+cr2+cr3+cr4+cr5))
pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7)) - pnorm((cr1+cr2+cr3+cr4+cr5+cr6))
pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7+cr8)) - pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7))
pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7+cr8+cr9)) - pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7+cr8))
pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7+cr8+cr9+cr10)) - pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7+cr8+cr9))

1 - pnorm((cr1+cr2+cr3+cr4+cr5+cr6+cr7+cr8+cr9+cr10))
"


fit_UVSDT <- fit.model(ID_dvector,textConnection(UVSDT),lower.bound=c(-Inf,rep(0,9),0,0.1),upper.bound=rep(Inf,12), n.optim=5, show.messages = FALSE)



fit_UVSDT$goodness.of.fit # goodness of fit
fit_UVSDT$parameters # parameters
```

