---
title: "R Notebook"
output:
  word_document: default
  pdf_document: default
  html_notebook: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For fitting the Block-Marschack and the other inequalities, we need a function that solves quadratic equations with inequality constraints. R
offers several such packages, see section 'Quadratic Optimization' on: https://cran.r-project.org/view=Optimization
Initially, we used the most popular package, quadprog (https://cran.r-project.org/package=quadprog) for this purpose. However, in some cases the function got stuck. Consequently, we tried other packages. Frr example, we observed good, albeit slow, results with Dykstra (https://cran.r-project.org/package=Dykstra). So all results reported here should replicate with Dykstra as well. We finally settled on quadprogpp which is a new and fast implementation of quadprog, which currently is only available from github: https://github.com/fnoorian/quadprogpp  It requires a C++ compiler (e.g., Rtools on Windows or Xtools on Mac) and can then be installed via devtools

```{r Packages, include=FALSE,  results="hide"}

library("psych", lib.loc="~/R/win-library/3.5")
library("tidyverse", lib.loc="~/R/win-library/3.5")
library("jsonlite", lib.loc="~/R/win-library/3.5")

#if (!(require("devtools"))) install.packages("devtools")
#devtools::install_github("fnoorian/quadprogpp", force = TRUE)
library("quadprogpp", lib.loc="~/R/win-library/3.5") ## for fitting Block-Marschak

```

```{r data wrangling, include=FALSE}
setwd("C:/Users/mccormick/GitHub/PhD-Thesis")

data1 <- read.csv("data/Block Marschak Experiment/b_m_data.csv")
data2 <- read.csv("data/Block Marschak Experiment/experiment3data.csv")


din1 <- data1 %>%
  select(uid,Test_T1_lineupSize, Test_T1_originalIdentification, demographics_age, demographics_gender, demographics_country) %>%
  filter(!is.na(Test_T1_lineupSize)& demographics_country == "USA")

din2 <- data2 %>%
  select(uid,Rank_T1_lineupSize, Rank_T1_originalIdentification, demographics_age, demographics_gender, demographics_country,condition)%>%
  filter(!is.na(Rank_T1_lineupSize)& demographics_country == "USA" & condition %in% c("S_H_P","S_L_P")) %>%
  select(-condition) %>%
  rename(Test_T1_lineupSize = Rank_T1_lineupSize,
         Test_T1_originalIdentification = Rank_T1_originalIdentification
         )

din <- rbind(din1,din2)
```


##################################################################
##                         Demographics                         ##
##################################################################
```{r demographics}
#length(unique(din$uid))

describe(din$demographics_age)

demo <- din %>% 
  select(demographics_age, demographics_gender, demographics_country)# %>% 

demo %>% 
  select(-demographics_age) %>%
  map(~prop.table(table(.)))
```
##################################################################
##                         Prepare Data                         ##
##################################################################

Create vector of CID FID counts for each lineup size. Note that each lineup size has a different number of observations.

```{r,echo=FALSE}
din$correct <- if_else(din$Test_T1_originalIdentification == "F68", 1, 0)
din$n <- if_else(!is.na(din$Test_T1_originalIdentification) == "F68",1,0)


dat <- din %>% 
  group_by(Test_T1_lineupSize) %>%
  summarise(correct = sum(correct),
            n = n())

dvector <- dat %>% 
  group_by(Test_T1_lineupSize) %>%
  summarise(corr = sum(correct),
            incorrect = sum(n) - sum(correct)) %>% 
  select(-Test_T1_lineupSize) %>% 
  as.matrix() %>% 
  t() %>% 
  as.vector

dvector


```
Create vector of CID for each lineup size

```{r, echo=FALSE}
prop_vector <- dat %>% 
  group_by(Test_T1_lineupSize) %>% 
  summarise(out = sum(correct)/sum(n)) %>% 
  {.$out}

prop_vector
```

##################################################################
##                      Fit Block-Marschak                      ##
##################################################################

## inequality matrix ##
```{r, echo=FALSE}
MM <- structure(c(2, 3, 4, 5, 6, 7, 8, 2, 3, 4, 5, 6, 7, 8, 3, 4, 5, 
6, 7, 8, 4, 5, 6, 7, 8, 5, 6, 7, 8, 6, 7, 8, 7, 8, 8, 3, 4, 5, 
6, 7, 8, -1, -1, -1, -1, -1, -1, -1, 1, 0, 0, 0, 0, 0, 0, -1, 
0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 
1, 0, 0, 1, 0, 1, -2, -3, -4, -5, -6, -7, 0, 0, 0, 0, 0, -7, 
14, 0, 1, 0, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 
0, -2, 1, 0, 0, 0, -3, 1, 0, 0, -4, 1, 0, -5, 1, -6, 1, 3, 6, 
10, 15, 21, 0, 0, 0, 0, -21, 63, -63, 0, 0, 1, 0, 0, 0, 0, 0, 
0, -1, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 1, -2, 1, 0, 0, 3, -3, 
1, 0, 6, -4, 1, 10, -5, 15, 0, -1, -4, -10, -20, -35, 0, 0, 0, 
-35, 140, -210, 140, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, -1, 0, 0, 
0, 0, 0, -1, 1, 0, 0, 0, 1, -2, 1, 0, -1, 3, -3, 1, -4, 6, -4, 
-10, 10, -20, 0, 0, 1, 5, 15, 35, 0, 0, -35, 175, -350, 350, 
-175, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 
1, 0, 0, 0, 1, -2, 1, 0, -1, 3, -3, 1, -4, 6, 5, -10, 15, 0, 
0, 0, -1, -6, -21, 0, -21, 126, -315, 420, -315, 126, 0, 0, 0, 
0, 0, 1, 0, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 1, 0, 0, 0, 
1, -2, 0, 0, -1, 3, 0, 1, -4, -1, 5, -6, 0, 0, 0, 0, 1, 7, -7, 
49, -147, 245, -245, 147, -49, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 
0, 0, 0, -1, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 1, 0, 0, 0, -1, 0, 
0, 1, 0, -1, 1, 0, 0, 0, 0, 0, -1, 8, -28, 56, -70, 56, -28, 
8, 0.5, 0.333333333333333, 0.25, 0.2, 0.166666666666667, 0.142857142857143, 
0.125, -1, -1, -1, -1, -1, -1, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, -1, -1, -1, -1, -1, -1, 0, 
0, 0, 0, 0, 0, 1), .Dim = c(48L, 9L), .Dimnames = list(NULL, 
    c("max", "2AFC", "3AFC", "4AFC", "5AFC", "6AFC", "7AFC", 
    "8AFC", "RHS")))
MM
```

##Fitting to the Block Marschak inequalities

Closest fitting expected data that respect the Block-Marschak inequalities:
```{r, echo=FALSE}
qpfit_BM   <- -1*QP.Solve(
  G = diag(7), #n by n matrix appearing in the quadratic function to be minimized.
  g0 = prop_vector, #vector on length n appearing in the quadratic function to be minimized.
  CI = -1*t(MM[-c(42:48),-c(1,9)]), #n by m constraints matrix. 
  ci0 = -1*MM[-c(42:48),9] #constraints constants, with size m. 
  )
qpfit_BM


```

##Introduction of the monotonic likelihood constraint

Closest fitting expected data that respect the Block-Marschak inequalities and the monotonic likelihood constraint:

```{r, echo=FALSE}
qpfit_BMML <- -1*QP.Solve(
  G = diag(7), 
  g0 = prop_vector, 
  CI = -1*t(MM[,-c(1,9)]), 
  ci0 = -1*MM[,9]
  )
qpfit_BMML

```


## yields rankings

reconstructing the CID and FID(respectively) from the m-AFC data:

```{r, echo=FALSE}

binom <- choose(7,0:7)  #creates vector of binomial coefficients for n=7 {1,7,21,35,35,21,7,1}
MM8 <- MM[MM[,"max"] == 8,][-c(2),-c(1,9)] #selects from MM: rows where max=8 and removes second of these max=8 rows, then removes columns "max" and "RHS"
prod <- c(MM8%*%qpfit_BMML) #matrix multiplication, including diffnet objects
A <- c(rep(0,7),1) #creates vector {0,0,0,0,0,0,0,1}

rnko <- c(binom *(prod + A ))
#rnko
cumsum(rnko)

rnkn <- (1-rnko)/7
#rnkn
cumsum(rnkn)

```
## G-square:
```{r, echo=FALSE}
getGsq <- function(Q,dd){
  size <- c(sum(dvector[1:2]),
          sum(dvector[1:2]), 
          sum(dvector[3:4]),
          sum(dvector[3:4]),
          sum(dvector[5:6]), 
          sum(dvector[5:6]),
          sum(dvector[7:8]),
          sum(dvector[7:8]),
          sum(dvector[9:10]), 
          sum(dvector[9:10]),
          sum(dvector[11:12]),
          sum(dvector[11:12]),
          sum(dvector[13:14]),
          sum(dvector[13:14])
          )
  ee <- c(rbind(Q, 1-Q))*size
  # compute Gsq
  #Gsq <- 2*sum(dd[dd!=0]*(log(dd[dd!=0])-log(ee[dd!=0])))
    Gsq <- 2*sum(dd[dd!=0]*(log((dd[dd!=0])/(ee[dd!=0]))))

  return(Gsq)
}
```

# Block- Marschak
```{r, echo=FALSE}
fitdata_BM <- getGsq(qpfit_BM, dvector)
fitdata_BM
```


# Block-Marschak with monotonic likelihood
```{r, echo=FALSE}
fitdata_BMML <- getGsq(qpfit_BMML, dvector)
fitdata_BMML

```
### multiplicative inequalities 
```{r, echo=FALSE}
epc <- c(1,qpfit_BMML)

all(c(
epc[3] > epc[2]**2  ,        # 2 > 1+1
epc[4] > epc[2]**3   ,       # 3 > 1+1+1
epc[4] > epc[2]*epc[3] ,      # 3 > 1+2
epc[5] > epc[2]**4     ,     # 4 > 1+1+1+1
epc[5] > epc[3]*epc[2]**2  ,  # 4 > 2+1+1
epc[5] > epc[3]**2     ,     # 4 > 2+2
epc[5] > epc[4]*epc[2] ,      # 4 > 3+1
epc[6] > epc[2]**5     ,     # 5 > 1+1+1+1+1
epc[6] > epc[2]**3*epc[3] ,   # 5 > 2+1+1+1
epc[6] > epc[3]**2*epc[2],    # 5 > 2+2+1
epc[6] > epc[4]*epc[2]**2 ,   # 5 > 3+1+1
epc[6] > epc[4]*epc[3] ,      # 5 > 3+2
epc[6] > epc[5]*epc[2] ,      # 5 > 4+1
epc[7] > epc[2]**6   ,       # 6 > 1+1+1+1+1+1
epc[7] > epc[3]*epc[2]**4 ,   # 6 > 2+1+1+1+1
epc[7] > epc[3]**2*epc[2]**2, # 6 > 2+2+1+1
epc[7] > epc[3]**3   ,       # 6 > 2+2+2
epc[7] > epc[4]*epc[2]**3 ,   # 6 > 3+1+1+1
epc[7] > epc[4]*epc[3]*epc[2], # 6 > 3+2+1
epc[7] > epc[4]**2    ,      # 6 > 3+3
epc[7] > epc[5]*epc[2]**2 ,   # 6 > 4+1+1
epc[7] > epc[5]*epc[3] ,      # 6 > 4+2
epc[7] > epc[6]*epc[2]  ,     # 6 > 5+1
epc[8] > epc[2]**7  ,               # 7 > 1+1+1+1+1+1+1
epc[8] > epc[3]*epc[2]**5 ,          # 7 > 2+1+1+1+1+1
epc[8] > epc[3]**2*epc[2]**3 ,       # 7 > 2+2+1+1+1
epc[8] > epc[3]**3*epc[2]  ,         # 7 > 2+2+2+1
epc[8] > epc[4]*epc[2]**4  ,         # 7 > 3+1+1+1+1
epc[8] > epc[4]*epc[3]*epc[2]**2 ,    # 7 > 3+2+1+1
epc[8] > epc[4]*epc[3]**2,           # 7 > 3+2+2
epc[8] > epc[4]**2*epc[2] ,          # 7 > 3+3+1
epc[8] > epc[5]*epc[2]**3,           # 7 > 4+1+1+1
epc[8] > epc[5]*epc[3]*epc[2] ,       # 7 > 4+2+1
epc[8] > epc[5]*epc[4] ,             # 7 > 4+3
epc[8] > epc[6]*epc[2]**2 ,          # 7 > 5+1+1
epc[8] > epc[6]*epc[3] ,             # 7 > 5+2
epc[8] > epc[7]*epc[2]               # 7 > 6+1
))

## Therefore, G-Square equal to 0, p-value equal to 1.


```
Therefore, G-Square equal to 0, p-value equal to 1.

##---------------------------------------------------------------
##                    get bootstrap p-value                     -
##---------------------------------------------------------------
```{r, echo=FALSE}

nsim     <- 100000
gfitdata_BM   <- vector("numeric", nsim)
gfitdata_BMML <- vector("numeric", nsim)

get_np_sample <- function(dvec) {
  out <- vector("numeric", length(dvec))
  for (i in seq_len(length(dvec)/2)) {
    sel <- (i-1)*2 + (1:2)
    out[sel] <- rmultinom(1, sum(dvec[sel]), dvec[sel]/sum(dvec[sel]) )[,1]
  }
  out
}

get_p_sample <- function(dvec, prob) {
  out <- vector("numeric", length(dvec))
  for (i in seq_len(length(dvec)/2)) {
    sel <- (i-1)*2 + (1:2)
    out[sel] <- rmultinom(1, sum(dvec[sel]), c(prob[i], 1-prob[i]) )[,1]
  }
  out
}

set.seed(666)
for(iii in 1:nsim){
size <- c(sum(dvector[1:2]),  
          sum(dvector[3:4]), 
          sum(dvector[5:6]), 
          sum(dvector[7:8]), 
          sum(dvector[9:10]), 
          sum(dvector[11:12]),
          sum(dvector[13:14])
          )
  gdd <- get_np_sample(dvector)
  
  g_qpfit <- -1*QP.Solve(diag(7), gdd[seq(1,13,2)]/size, 
                         -1*t(MM[-c(42:48),-c(1,9)]), -1*MM[-c(42:48),9])
  
  
  gdd <- get_p_sample(dvector, g_qpfit)
  
   g_qpfit <- -1*QP.Solve(diag(7), gdd[seq(1,13,2)]/size, 
                          -1*t(MM[-c(42:48),-c(1,9)]), -1*MM[-c(42:48),9]) 
  
  
  gfitdata_BM[iii] <- getGsq(g_qpfit,gdd)
  
}
## p-value ##
mean(gfitdata_BM > fitdata_BM)
## [1] 0.98182
#describe(gfitdata_BM)
```

```{r}
set.seed(999)
for(iii in 1:nsim){
  size <- c(sum(dvector[1:2]),  
            sum(dvector[3:4]), 
            sum(dvector[5:6]), 
            sum(dvector[7:8]), 
            sum(dvector[9:10]), 
            sum(dvector[11:12]),
            sum(dvector[13:14])
            )
  gdd <- get_np_sample(dvector)
  
  g_qpfit <- -1*QP.Solve(diag(7), gdd[seq(1,13,2)]/size, 
                         -1*t(MM[,-c(1,9)]), -1*MM[,9])
  
  
  gdd <- get_p_sample(dvector, g_qpfit)
  
   g_qpfit <- -1*QP.Solve(diag(7), gdd[seq(1,13,2)]/size, 
                          -1*t(MM[,-c(1,9)]), -1*MM[,9]) 
  
  
  gfitdata_BMML[iii] <- getGsq(g_qpfit,gdd)
  
}
## p-value ##
mean(gfitdata_BMML > fitdata_BMML)


# [1] 0.92689
```

#################################################################
##                   Figure                                    ##
#################################################################

```{r}
library("grDevices", lib.loc="C:/Program Files/R/R-3.5.3/library")
library("graphics", lib.loc="C:/Program Files/R/R-3.5.3/library")
#dev.off()
dd <- dvector

par(mfrow=c(1,2))
h <- dd[seq(1,13,2)]
size <- c(sum(dd[1:2]),  
          sum(dd[3:4]), 
          sum(dd[5:6]), 
          sum(dd[7:8]), 
          sum(dd[9:10]), 
          sum(dd[11:12]),
          sum(dd[13:14])
          )
tpc <- dd[seq(1,13,2)]/size
#pdf("Figure_1.pdf", 8, 4.5)

par(pty="s")
plot(2:8,tpc,pch=15,cex=1.5,xlim=c(1.5,8.5),ylim=c(0,1),
     xlab="Choice Set Size (m)", ylab="Proportion Correct",
     cex.lab=1.3, main="m-AFC Performance",xaxs="i",yaxs="i")

cil <- tpc - 1.96*sqrt((tpc*(1-tpc))/sum(dd[1:2]))
ciu <- tpc + 1.96*sqrt((tpc*(1-tpc))/sum(dd[1:2]))

for(ii in 1:7) segments(ii+1,ciu[ii],ii+1,cil[ii])

polygon(rep(seq(1.5,8.5,1),each=2),c(0,rep(1/(2:8),each=2),0),
        col="lightgray",border = FALSE)
lines(rep(seq(1.5,8.5,1),each=2),c(0,rep(1/(2:8),each=2),0),lty=2)
box()
points(2:8,c((qpfit_BMML)),pch=21,cex=1,bg="darkgray")


legend(6, 0.9, legend=c("Data","BMI-ML"), 
       pch=c(15,21),col=rep("black",2), 
       pt.bg=c(NULL,"darkgray"), cex=1)
#dev.off()
```
#################################################################
##                            ROC                              ##
#################################################################
```{r}
#pdf("Figure_2.pdf", 8, 4.5)
par(pty="s")
plot(cumsum(rnkn),cumsum(rnko),typ="l",pch=16,xaxs="i",yaxs="i",
xlab="False Alarms", ylab="Hits",cex.lab=1.3, main="Yes-No ROC",lwd=2,
xlim=c(0,1), ylim=c(0,1),cex=1.3)
points(cumsum(rnkn),cumsum(rnko),pch=21,bg="darkgray",cex=1.3)
polygon(c(0,1,1),c(0,0,1),col="lightgray",border = FALSE)
abline(0,1,lty=2)
segments(0,1,0.5,0.5,lty=2)
box()

#dev.off()
```

