---
title: "Fitting the m-AFC eyewitness data to UV-SDT model"
author: "Kym McCormick"
date: "16 April 2019"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)



```

```{r, include=FALSE}
library("plyr", lib.loc="~/R/win-library/3.5")
library("dplyr", lib.loc="~/R/win-library/3.5")
library("nnet", lib.loc="~/R/win-library/3.5")
library("MPTinR", lib.loc="~/R/win-library/3.5")
library("psych", lib.loc="~/R/win-library/3.5")
#library("tseries", lib.loc="~/R/win-library/3.5")
library("DescTools", lib.loc="~/R/win-library/3.5")
```

Forced choice accuracy is given by 

   $P_C^{\langle k \rangle} = \int_{-\infty}^{\infty} g(x)F(x)^{n-1}dx$.
    


Step one is to find the best fitting UV-SDT model parameters to the empirical data. I adaped the following code from Kellen Supplemental script (2015)

```{r}
#Empirical data for lineup size k = {2,3,...,7,8}

BMIDataCID <- c(0.8862,	0.7616,	0.6737,	0.6491,	0.5606,	0.5498, 0.50276)

data_kafc <- c(rbind(BMIDataCID,1-BMIDataCID))*300

SDT_kafc <- function(Q, data, param.names, n.params, tmp.env, lower.bound, upper.bound){
   
    e<-vector(
      mode = "numeric",
      length = 4
      )

    mu <- Q[1]
    ss <- Q[2]
       
    rank <- function(i,k,mu=1,ss=1){
            f1 <- function(x,i,k,mu,ss) {
              choose(k -1, i-1)*dnorm(x,mu,ss)*pnorm(x)**(k-i)*(1-pnorm(x))**(i-1)    
              }        
            tmp <- vector(
              mode = "numeric",
              length = length(i)
              )
            for(ii in 1:length(i)) 
              tmp[ii] <- integrate(
                f = f1,
                lower = -Inf, 
                upper = Inf, 
                i = i[ii],
                k = k,
                mu = mu,
                ss = ss
                ) $value
            return(tmp)
    }
 

    e[1:2]  <- rank(1:2,2,mu=mu,ss=ss)    
    e[3:4]  <- c(rank(1,3,mu=mu,ss=ss), 1- rank(1,3,mu=mu,ss=ss))
    e[5:6]  <- c(rank(1,4,mu=mu,ss=ss), 1- rank(1,4,mu=mu,ss=ss) )
    e[7:8]  <- c(rank(1,5,mu=mu,ss=ss), 1- rank(1,5,mu=mu,ss=ss))
    e[9:10] <- c(rank(1,6,mu=mu,ss=ss), 1- rank(1,6,mu=mu,ss=ss) )
    e[11:12] <- c(rank(1,7,mu=mu,ss=ss), 1- rank(1,7,mu=mu,ss=ss) )
    e[13:14] <- c(rank(1,8,mu=mu,ss=ss), 1- rank(1,8,mu=mu,ss=ss) ) 
    #add this last line if you have k=8 kAFC data

    
    LL <- -sum(data[data!=0]*log(e[data!=0]))
    return(LL)
}


fit_kafc <- fit.mptinr(
  data = data_kafc, 
  objective = SDT_kafc, 
  param.names = c("mu", "sigma"), 
  categories.per.type = c(2,2,2,2,2,2,2), 
  lower.bound = c(0,0.1), 
  upper.bound = Inf, 
  n.optim = 5,
  show.messages = FALSE
  )

fit_kafc
```

Below is the code to simulate CIDs from the best fitting UV-SDT model parameters

```{r}
mu=1.3318149
ss=0.6336813
simulated <- vector("numeric")
rank <- function(i,k,mu=1.3318149,ss=0.6336813){
            f1 <- function(x,i,k,mu,ss) {
              choose(k -1, i-1)*dnorm(x,mu,ss)*pnorm(x)**(k-i)*(1-pnorm(x))**(i-1)    
              }        
            tmp <- vector(
              mode = "numeric",
              length = length(i)
              )
            for(ii in 1:length(i)) 
              tmp[ii] <- integrate(
                f = f1,
                lower = -Inf, 
                upper = Inf, 
                i = i[ii],
                k = k,
                mu = mu,
                ss = ss
                ) $value
            return(tmp)
}

simulated[1]  <- rank(1,2,mu=mu,ss=ss)    
simulated[2]  <- rank(1,3,mu=mu,ss=ss)
simulated[3]  <- rank(1,4,mu=mu,ss=ss)
simulated[4]  <- rank(1,5,mu=mu,ss=ss)
simulated[5] <- rank(1,6,mu=mu,ss=ss)
simulated[6] <- rank(1,7,mu=mu,ss=ss)
simulated[7] <- rank(1,7,mu=mu,ss=ss)
simulated
```

I realised then that I need to add in a G squared test of some sort (not sure if it is correct). I don't really understand how this differs from the loglikelihood test used in the fitting....

```{r}
sim_kafc <- c(rbind(simulated,1-simulated))*300
matriz <- cbind(sim_kafc,data_kafc)
matriz
GTest(matriz)
```





